Just as with the simpler graphs we covered this semester (e.g., Trees,
LinkedLists) our graph must have some set of basic units.  For graphs these
units are the vertecies and the edges. Since we are implementing our graph with
an adjacency list we will need a method of indicating to which vertices a
vertex is connected and what the weight of that edge is, if applicable.  As
such, we will be building an inner class \lstinline|Edge<E>| that stores this
information on the destination and the weight. The adjacency list that results 
from this will be a lists of edges that exist with respect to a given vertex. 
As you will see in the starter files, this class is inner class within the 
encompassing \lstinline|ListGraph<E>| class since it has little utility
outside the context of constructing a list graph. In this case \lstinline|E|
will be the type of our vertecies since we are represnting the graph with
just an edgelist.

\subsubsection{Attributes}

The following attributes will be used for representing the edges of our class:
\begin{enumerate}
    \item \lstinline|final int weight|
    \item \lstinline|final E dest|  
\end{enumerate}
Both of these attributes should be declared as \lstinline|final| since, once
set, we will not be changing the values associated with an instance of an
\lstinline|Edge|.

\subsubsection{Constructors}

\paragraph{\lstinline|public Edge(E dest) { ... }|}: This constructor will be
used for the creation of edges for unweighted graphs; hence, the reason for the
absence of an integer parameter indicating the weight of the edge. It should
therefore set the \lstinline|weight| attribute to zero when a new edge is
instantiated using this constructor. The \lstinline|dest| parameter is generic
and will contain a reference to the destination object.

\paragraph{\lstinline|public Edge(E dest, int weight) { ... }|} This
constructor is similar to the former one but adds a primitive integer parameter
\lstinline|weight|. As such, this constructor will be used for the construction
of weighted edges and should set the \lstinline|dest| and \lstinline|weight| 
attributes of the object equal to the parameters passed through the function.
